---
title: "simpleRegress"
author: Aylin Torres
date: 11/12/24
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

If comparing all the models other than neck for lenght the worst model for determining Length is age with a adjusted R-squared number of 0.5073, the Headwth with a the number .5321, followed by the weight at 0.7423, CHEST at .7869, and lastly HEADLEN with an adjusted R-Squared number of 0.8434. This would mean than HEANLEN is the most reliable model for predicting LENGHT.


